Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-10 emsoft-2019/Error_Analysis.tex
Rocco: Error Analysis symbols

We thus have to ensure that these errors remain below the error bound $\Delta$
used to design the robust MPC controller:
\begin{align}\label{eq:delta}
  \max_{\forall i,j. neighbour(\mathcal{R}_{i},\mathcal{R}_{j})}|u_{i}-u_{j}| + \max_{\forall i.\mathcal{R}_{i}\in\mathcal{R}} err(u_{i})_{p} \le \Delta
\end{align}
where $i,j$ are the indexes of two generic regions $\mathcal{R}_{i}$ and
$\mathcal{R}_{j}$, \\ $neighbour(\mathcal{R}_{i},\mathcal{R}_{j})$ states that
two regions share at least a point, $u_{i}$ is the
control action for controller $i$, and $err(u_{i})_{p}$ is
the approximation error for computing the activation function $u_{i}$ in fixed precision using p bits format.
\paragraph{Incorrect Region Selection}

The first part of the error in~\autoref{eq:delta} captures the error due to
selection of the wrong control action, i.e. with infinite-precision arithmetic
and in the absence of any uncertainty from hardware measurements we would choose
control action $u_i$, but due to uncertainties we actually choose control action $u_j$:
\begin{align} \label{eq:maximization}
  &\max_{\forall i,j.neighbour(\mathcal{R}_{i},\mathcal{R}_{j})}|u_{i}-u_{j}|= \\
  &\max_{\forall i,j.neighbour(\mathcal{R}_{i},\mathcal{R}_{j})}|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|\nonumber
\end{align}

@@

A naive computation of this error would consider all possible values of $x_k$.
This would lead to a gross over-approximation, however, since the controller
will choose a wrong region only in a relative narrow neighbourhood, or
\emph{tube}, around the boundary between two regions $R_i$ and $R_j$.
In~\autoref{eq:maximization}, we thus constrain $x_k$ to be within an appropriate tube:
\begin{equation}\label{eq:tube}
(border_{i,j} >= -\varepsilon) \land (border_{i,j} <= \varepsilon)
\end{equation}
where $border_{i,j}$ constrains $x_k$ to be on the border between two regions
$R_i$ and $R_j$ and $\varepsilon$ captures the uncertainty in computing the
correct region.

\eva{The below, I believe, is somehow defining $border_{i,j}$, but I don't understand
how. Please explicitly define $border_{i,j}$.}
In formula $\exists\; m,n \;$such that:
\begin{equation}
border_{i,j}=(H_{i}\statevar-K_{j})_{m} = (H_{j}\statevar-K_{j})_{n}
\end{equation}
where $m$ and $n$ are the indexes of the matching border respectively in $\mathcal{R}_{i}$ and $\mathcal{R}_{j}$.

>>>>

We thus have to ensure that these errors remain below the error bound $\delta$
used to design the robust MPC controller:
\begin{align}\label{eq:delta}
  \max_{\forall i,j. \mathit{neighbour}(\mathcal{R}_{i},\mathcal{R}_{j})}|u_{i}-u_{j}| + \max_{\forall i.\mathcal{R}_{i}\in\mathcal{R}} err(u_{i})_{p} \le \delta
\end{align}
where $i,j$ are the indexes of two generic regions $\mathcal{R}_{i}$ and
$\mathcal{R}_{j}$, \\ $\mathit{neighbour}(\mathcal{R}_{i},\mathcal{R}_{j})$ states that
two regions share at least a point, $u_{i}$ is the
control action for controller $i$, and $err(u_{i})_{p}$ is
the approximation error for computing the activation function $u_{i}$ in fixed precision using p bits format.
\paragraph{Incorrect Region Selection}

The first part of the error in~\autoref{eq:delta} captures the error due to
selection of the wrong control action, i.e. with infinite-precision arithmetic
and in the absence of any uncertainty from hardware measurements we would choose
control action $u_i$, but due to uncertainties we actually choose control action $u_j$:
\begin{align} \label{eq:maximization}
  &\max_{\forall i,j.\mathit{neighbour}(\mathcal{R}_{i},\mathcal{R}_{j})}|u_{i}-u_{j}|= \\
  &\max_{\forall i,j.\mathit{neighbour}(\mathcal{R}_{i},\mathcal{R}_{j})}|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|\nonumber
\end{align}

@@

A naive computation of this error would consider all possible values of $x_k$.
This would lead to a gross over-approximation, however, since the controller
will choose a wrong region only in a relative narrow neighbourhood, or
\emph{tube}, around the boundary between two regions $R_i$ and $R_j$.
In~\autoref{eq:maximization}, we thus constrain $x_k$ to be within an appropriate tube:
\begin{equation}\label{eq:tube}
(\mathit{border}_{i,j} \ge -\varepsilon) \land (\mathit{border}_{i,j} \le \varepsilon)
\end{equation}
where $\mathit{border}_{i,j}$ constrains $x_k$ to be on the border between two regions
$R_i$ and $R_j$ and $\varepsilon$ captures the uncertainty in computing the
correct region.

\eva{The below, I believe, is somehow defining $border_{i,j}$, but I don't understand
how. Please explicitly define $border_{i,j}$.}
In formula $\exists\; m,n \;$such that:
\begin{equation}
\mathit{border}_{i,j}=(H_{i}\statevar-K_{j})_{m} = (H_{j}\statevar-K_{j})_{n}
\end{equation}
where $m$ and $n$ are the indexes of the matching border respectively in $\mathcal{R}_{i}$ and $\mathcal{R}_{j}$.
